---
title       : Projections Project
subtitle    : Defining Data Products - Assignment
author      : Ian
job         : BugBunny
framework   : revealjs     # {io2012, html5slides, shower, dzslides, ...}
revealjs    :
  theme     : sky
  transition: cube
  center    : "true"
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : zenburn      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
logo        : Screenshot3.png
---

## Projections Project
<br>
### Developing Data Products 
### Assignment
<br><br>
### Ian
BugBunny

---

### Population Projections
### for the UK

* The assignment was to code and deploy an interactive web app using the R package _shiny_.

* 'Demography is destiny' according to Auguste Comte, or maybe Wattenberg and Scammon (1970).

* This app computes population projections for the United Kingdom for 2015-50 using forecasts of total fertility chosen by the user. It can produce a population pyramid for the mid- or end-point of any decade within this period that the user selects.

* Thereby, it enables the user to visualize how changes in the birth rate might affect the future size and age structure of the British population.

---

### A ___static___ population pyramid

```{r echo=FALSE}
Men <- c(2059, 2021, 1813, 1962, 2203, 2240, 2179, 2029, 2124,
    2280, 2249, 1949, 1713, 1754, 1295, 992, 679, 368, 163)
Women <- c(1959, 1928, 1730, 1858, 2117, 2215, 2203, 2046, 2169,
    2346, 2312, 1999, 1785, 1858, 1428, 1170, 905, 603, 384)
agelab <- c("0-4","5-9","10-14","15-19","20-24","25-29","30-34",
  "35-39","40-44","45-49","50-54","55-59","60-64","65-69","70-74",
  "75-79","80-44","85-89", "90+")
```

```{r}
library(plotrix); par(mar = pyramid.plot(Men, Women, gap = 250,  
   lxcol = "steelblue", rxcol = "plum", unit = "000s", labels = agelab,
   main = "United Kingdom", top.labels = c("Men", "2015", "Women")))
```

---

### The power of _shiny_

<br>

<p style="text-align: left;"> The app demonstrates several features of <em>shiny:</em></p>

<br>

* <div class="fragment"> Panelled web page layouts, including tabbed panels</div>
* <div class="fragment"> Use of widgets for input (sliders, dropdown boxes)</div>
* <div class="fragment"> Reactive code that runs if the sliders change, but not when the dropdown box does</div>
* <div class="fragment"> Two types of reactive output (text and a chart)</div>
* <div class="fragment"> Web hosting on the shiny apps server</div>

---

### Accessing the app and the code

<br>

The app is hosted on _RStudio_'s shiny apps server:  
https://bugbunny.shinyapps.io/ProjectionsProject  

<br>

The R scripts containing the code are on GitHub:  
https://github.com/BugBunny/ProjectionsProject

<br>

<p style="font-size: 50%;">Projections App. Copyright (C) 2015 - Ian Timaeus</p> 
<p style="font-size: 50%;">This program comes with ABSOLUTELY NO WARRANTY;
this is free software, and you are welcome to redistribute it
under certain conditions; see http://www.gnu.org/licenses/gpl.html</p>
